### 2016-02-12 prepReport/workPlan.tex
Implemented the Ivo suggested corrections

\section{Approach and  Main Tasks}
Dwight Eisenhower, United States' President from 1953 to 1961 and Army Officer, said that `no battle was ever won according to plan, but no battle was ever won without one'. Hence, although this initial planning draft might not be religiously followed in all its extent, it is important to break down the work in \textbf{tasks} so that I and my supervisors can keep track of what has to be done, and establishing deadlines for the small achievements that, together, will build up to the succesful completion of the proposed work of this thesis. The detailed explanation of each task is provided in Section~\ref{sec:wp_tasks_td} and the \textbf{schedule} for them, where their approximate begin and end weeks are marked, is represented by a \emph{Gantt Chart} in Section~\ref{sec:wp_tasks_gantt}.

\subsection{Task Description}\label{sec:wp_tasks_td}
The work will be partitioned in \emph{five} large groups of tasks, and each of these groups will be further partitioned in smaller subtaskswhich are the actual assignements that I will be completing. We can think of the group of task as a sort of \emph{logical} grouping of the subtasks, according both to their relatedness and also to their precedence relationships. The task groups, and their related subtasks, are as follows

\begin{itemize}
    \item \textbf{T1 -- Preparation} -- This stage is the initial phase of the work, where I will essentialy setup my working environment and finish the Python modules for the LSTM network that will be used in the validation of my Verilog modules

        \begin{itemize}
            \item \textbf{T1.1 -- Complete Python Class with SPSA} -- here I will finish the Python modules that I have already developed as a preparation for this work, whose details are presented in Section~\ref{chap:earlyWork}, by adding the SPSA training algorithm, as opposed to the current Backpropagation Throgh Time version.

@@

            \item \textbf{T1.3 -- Setup FPGA Development Board} -- this is a farily technical step, where I setup my working environment, and make sure that everything is working correctly and is properly configured. As will be pointed out in Section~\ref{sec:wp_sh}, the FPGA development board of choice will be Xilinx~\textregistered Zedboard.

@@

            \item \textbf{T2.2 -- Design SPSA Module} -- this task comprises the Verilog description of the module that will update the network weights using SPSA, and also the development of a testbench to validate my description. Furthermore, I will compare the output of this model with the golden output produced by a standalone SPSA Python Class previously developed in \textbf{T1}.
            \item \textbf{T2.3 -- Design LSTM Neuron/Layer Module} -- similar to the previous task, but now I am aiming to implement the actual LSTM Neuron or a layer of LSTM Neurons. This is a design decision that will need to be set in \textbf{T2.1}, to asses whether it is justifiable to have dedicated multiplication units assigned to each neuron, or we can perform matrix-like batch multiplications and treat the LSTM as a batch of Neurons, i.e. as a layer. Like in the previous task, a testbench will also be developed, and the module validate both with it and the Python golden output.

@@

        \begin{itemize}
            \item \textbf{T3.1 -- Synthesis of the SPSA Module} -- the module developed in \textbf{T2.2} is now syet
                {bar height=.6}thesized and validated
            \item \textbf{T3.2 -- Synthesis of the LSTM Neuron/Layer Module} -- same as the previous task, but now on the module of \textbf{T2.3}
            \item \textbf{T3.3 -- Integration of the Modules and Validation} -- the modules synthesized in the previous tasks are integrated and validated using the same testbench as in \textbf{T2.4}.
        \end{itemize}

    \item \textbf{T4 -- Benchmarking the Design} -- at this stage, we have a fully functional FPGA design of an LSTM network with SPSA on-chip training. Henceforth, we will need to benchmark its performance by comparing it to~\cite{Tavear13, Hochreiter07}, and prove its usefulness by using it in one or two usecases from~\ref{chap:stateArt}, which are interesting uses of Deep Learning techniques such as these.

        \begin{itemize}
            \item \textbf{T4.1 -- Benchmark the Performance/Computing Time} -- perform a side-by-side comparison of our model with the software counterpart of\cite{Tavear13, Hochreiter07} and with the only hardware implementation of LSTM of~\cite{Chang15}.
            \item \textbf{T4.2 -- Reproduce some of the state of the art applications of LSTM} -- in order to be able to show real-life, user-oriented, applications, I understand it is a good idea to try to reproduce some of the state of the art usages of LSTM, outlined in Section~\ref{chap:sa_apps}. It is too early to commit myself to which of these applications I will use, and how many, because that will depend on how well the work on tasks \textbf{T2} and \textbf{T3} is flowing. Nevertheless, I intend to at least impement one or two of them.
        \end{itemize}

    \item \textbf{T5 -- Write the Dissertation Final Report} -- while all the stages of work are developing, this task will obviously be active, by documenting all the design decisions, milestones acheieved and logging all the results that come from the implementation. A couple of weeks before the deadline, this will be the only active task, since producing a clear and well-written document requires concentration and undivided attention.

@@

\subsection{Hardware Resources}
The main hardware resource that I will use for my solution is the \textbf{Xilinx\textregistered~ Zedboard} (Figure~\ref{fig:zedboard}, whose core is a Zynq-7000 System-on-Chip that features both an FPGA core and an ARM \textregistered~ Cortex\texttrademark~-A9 processor. It is an FPGA development board that features several I/O interfaces such as Etherner, HDMI output, VGA output, Audio IOs, USB and UART, among other capabilites, making it easy to prototype additional features to the core design (i.e. for building the note transcription system of~\cite{Bock12}, and to make it operate in real-time, I would need an audio input, which I can easily get from the Audio IO, without investing time in connecting the codec and programming the FPGA to interface it).

@@

To write the final Disseration report, I will use \LaTeX (this report itself was also written in \LaTeX), and mostly use Tikz, Inkscape and Matplotlib to produce figures and drawings. Once again, all of this is free to use.

>>>>

\section{Approach and  Main Tasks}
Dwight Eisenhower, United States' President from 1953 to 1961 and Army Officer, said that `no battle was ever won according to plan, but no battle was ever won without one'. Hence, although this initial planning draft might not be religiously followed in all its extent, it is important to break down the work in \textbf{tasks} so that I and my supervisors can keep track of what has to be done, and establishing deadlines for the small achievements that, together, will build up to the successful completion of the proposed work of this thesis. The detailed explanation of each task is provided in Section~\ref{sec:wp_tasks_td} and the \textbf{schedule} for them, where their approximate begin and end weeks are marked, is represented by a \emph{Gantt Chart} in Section~\ref{sec:wp_tasks_gantt}.

\subsection{Task Description}\label{sec:wp_tasks_td}
The work will be partitioned in \emph{five} large groups of tasks, and each of these groups will be further partitioned in smaller subtasks which are the actual assignments that I will be completing. We can think of the group of task as a sort of \emph{logical} grouping of the subtasks, according both to their relatedness and also to their precedence relationships. The task groups, and their related subtasks, are as follows

\begin{itemize}
    \item \textbf{T1 -- Preparation} -- This stage is the initial phase of the work, where I will essentially setup my working environment and finish the Python modules for the LSTM network that will be used in the validation of my Verilog modules

        \begin{itemize}
            \item \textbf{T1.1 -- Complete Python Class with SPSA} -- here I will finish the Python modules that I have already developed as a preparation for this work, whose details are presented in Section~\ref{chap:earlyWork}, by adding the SPSA training algorithm, as opposed to the current Backpropagation Through Time version.

@@

            \item \textbf{T1.3 -- Setup FPGA Development Board} -- this is a fairly technical step, where I setup my working environment, and make sure that everything is working correctly and is properly configured. As will be pointed out in Section~\ref{sec:wp_sh}, the FPGA development board of choice will be Xilinx~\textregistered Zedboard.

@@

            \item \textbf{T2.2 -- Design SPSA Module} -- this task comprises the Verilog description of the module that will update the network weights using SPSA, and also the development of a testbench to validate my description. Furthermore, I will compare the output of this model with the golden output produced by a standalone SPSA Python Class previously developed in \textbf{T1}.
            \item \textbf{T2.3 -- Design LSTM Neuron/Layer Module} -- similar to the previous task, but now I am aiming to implement the actual LSTM Neuron or a layer of LSTM Neurons. This is a design decision that will need to be set in \textbf{T2.1}, to assess whether it is justifiable to have dedicated multiplication units assigned to each neuron, or we can perform matrix-like batch multiplications and treat the LSTM as a batch of Neurons, i.e. as a layer. Like in the previous task, a testbench will also be developed, and the module validate both with it and the Python golden output.

@@

        \begin{itemize}
            \item \textbf{T3.1 -- Synthesis of the SPSA Module} -- the module developed in \textbf{T2.2} is now synthesized and validated.
            \item \textbf{T3.2 -- Synthesis of the LSTM Neuron/Layer Module} -- same as the previous task, but now on the module of \textbf{T2.3}
            \item \textbf{T3.3 -- Integration of the Modules and Validation} -- the modules synthesized in the previous tasks are integrated and validated using the same testbench as in \textbf{T2.4}.
        \end{itemize}

    \item \textbf{T4 -- Benchmarking the Design} -- at this stage, we have a fully functional FPGA design of an LSTM network with SPSA on-chip training. Henceforth, we will need to benchmark its performance by comparing it to~\cite{Tavear13, Hochreiter07}, and prove its usefulness by using it in one or two use-cases from~\ref{chap:stateArt}, which are interesting uses of Deep Learning techniques such as these.

        \begin{itemize}
            \item \textbf{T4.1 -- Benchmark the Performance/Computing Time} -- perform a side-by-side comparison of our model with the software counterpart of~\cite{Tavear13, Hochreiter07} and with the only hardware implementation of LSTM of~\cite{Chang15}.
            \item \textbf{T4.2 -- Reproduce some of the state of the art applications of LSTM} -- in order to be able to show real-life, user-oriented, applications, I understand it is a good idea to try to reproduce some of the state of the art usages of LSTM, outlined in Section~\ref{sec:sa_apps}. It is too early to commit myself to which of these applications I will use, and how many, because that will depend on how well the work on tasks \textbf{T2} and \textbf{T3} is flowing. Nevertheless, I intend to at least implement one or two of them.
        \end{itemize}

    \item \textbf{T5 -- Write the Dissertation Final Report} -- while all the stages of work are developing, this task will obviously be active, by documenting all the design decisions, milestones achieved and logging all the results that come from the implementation. A couple of weeks before the deadline, this will be the only active task, since producing a clear and well-written document requires concentration and undivided attention.

@@

\subsection{Hardware Resources}
The main hardware resource that I will use for my solution is the \textbf{Xilinx\textregistered~ Zedboard} (Figure~\ref{fig:zedboard}, whose core is a Zynq-7000 System-on-Chip that features both an FPGA core and an ARM \textregistered~ Cortex\texttrademark~-A9 processor. It is an FPGA development board that features several I/O interfaces such as Ethernet, HDMI output, VGA output, Audio IOs, USB and UART, among other capabilities, making it easy to prototype additional features to the core design (i.e. for building the note transcription system of~\cite{Bock12}, and to make it operate in real-time, I would need an audio input, which I can easily get from the Audio IO, without investing time in connecting the codec and programming the FPGA to interface it).

@@

To write the final Dissertation report, I will use \LaTeX (this report itself was also written in \LaTeX), and mostly use Tikz, Inkscape and Matplotlib to produce figures and drawings. Once again, all of this is free to use.
